Effectiveness of BNT162b2 booster doses in England: an observational study in OpenSAFELY-TPP

### 2022-03-28 manuscript/draft-manuscript.Rmd
Update draft-manuscript.Rmd

There were `r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="postest", fup_period=="All") %>% pull(events))` positive SARS-CoV-2 tests,
`r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="covidadmitted", fup_period=="All") %>% pull(events))` COVID-19 hospital admissions, 
`r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="coviddeath", fup_period=="All") %>% pull(events))` COVID-19 deaths, 
and `r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="noncovidadmitted", fup_period=="All") %>% pull(events))` non-COVID-19 deaths 
across `r label_number(1, big.mark=",")((filter(incidences, treatment=="pfizer", outcome=="coviddeath", fup_period=="All") %>% pull(yearsatrisk)) * 365.25/7)` person-weeks of follow-up. 
The 10-week risk of positive SARS-CoV-2 test was `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` per 1000 in the boosted group 
and `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` in the unboosted group, 
representing a risk difference of `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=1000))` per 1000. 
For COVID-19 hospital admission, this was `r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
respectively (`r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events in the boosted group). 
For COVID-19 death it was `r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
(`r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events), 
and for non-COVID-19 death it was `r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
(`r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events) respectively  (Table 2).

>>>>

There were `r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="postest", fup_period=="All") %>% pull(events))` positive SARS-CoV-2 tests,
`r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="covidadmitted", fup_period=="All") %>% pull(events))` COVID-19 hospital admissions, 
`r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="coviddeath", fup_period=="All") %>% pull(events))` COVID-19 deaths, 
and `r label_number(1, big.mark=",")(filter(incidences, treatment=="pfizer", outcome=="noncoviddeath", fup_period=="All") %>% pull(events))` non-COVID-19 deaths 
across `r label_number(1, big.mark=",")((filter(incidences, treatment=="pfizer", outcome=="coviddeath", fup_period=="All") %>% pull(yearsatrisk)) * 365.25/7)` person-weeks of follow-up. 
The 10-week risk of positive SARS-CoV-2 test was `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` per 1000 in the boosted group 
and `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` in the unboosted group, 
representing a risk difference of `r km70 %>% filter(treatment=="pfizer", outcome=="postest", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=1000))` per 1000. 
For COVID-19 hospital admission, this was `r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
respectively (`r km70 %>% filter(treatment=="pfizer", outcome=="covidadmitted", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events in the boosted group). 
For COVID-19 death it was `r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
(`r km70 %>% filter(treatment=="pfizer", outcome=="coviddeath", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events), 
and for non-COVID-19 death it was `r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(risk_1) %>% (label_number(0.1, scale=1000))` 
and `r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(risk_0) %>% (label_number(0.1, scale=1000))` 
(`r km70 %>% filter(treatment=="pfizer", outcome=="noncoviddeath", subgroup=="none") %>% pull(kmrd) %>% (label_number(0.1, scale=-1000))` fewer events) respectively  (Table 2).
